---
title: "Monthly unit wide Endo-Histopathology Report"
author: "Endoscopy Dept"
date: "`r format(Sys.time(),'%d %B, %Y')`"
output: word_document
---

This is a monthly report summarising the endoscopy unit's activity:

Overall activity

```{r, fig.width=8,fig.height=8,echo=FALSE}

ggplot(ccByPerson,aes(x=Reason,y=ToTalNumBx))+
  geom_bar(stat="identity")+
  theme(axis.text.x=element_text(angle=-90))+
  labs(x="Date",title="Number of Biopsies taken by indication",y="Number of biopsies","Indication for biopsies")
  
```



```{r, fig.width=10,fig.height=12,echo=FALSE,fig.cap='Biopsies by endoscopist according to indication'}
pheatmap(matPoss,cluster_rows=F,fontsize=8,legend=F,cellwidth=8)

```



By endoscopist
```{r, fig.width=8,fig.height=8,echo=FALSE}
pheatmap(myEndoMatrix,cluster_rows=F,fontsize=8,legend=F,cellwidth=8)
```


```{r, fig.width=8,fig.height=8,echo=FALSE}
# ggplot(ProcedurePlot,aes(x=ProcPerformed,y=freq))+
#   geom_bar(stat="identity")+
#   geom_text(aes(label=freq),position=position_dodge(width=0.9),vjust=-0.35)+
#   theme(axis.text.x=element_text(angle=-90))+
#   labs(x="Procedure",title="Number of Procedures ",y="Number of Procedures")+
#    theme(legend.position="bottom")+
#   theme(legend.direction="horizontal")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r, fig.width=8,fig.height=8,echo=FALSE}
# ggplot(data=ProcedurePlot2,aes(x=ProcPerformed,freq,fill=Endo_Endoscopist))+
#   geom_bar(stat="identity")+
#   #coord_polar(theta="y")+
#   theme(legend.position="none")+
#   theme(axis.text.x=element_text(angle=-90))+
#    theme(legend.position="bottom")+
#   theme(legend.direction="horizontal")
```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r, fig.width=8,fig.height=8,echo=FALSE}
# ggplot(data=Gastroscopy,aes(x=ProcPerformed,freq,fill=Endo_Endoscopist))+
#   geom_bar(stat="identity")+
#    theme(legend.position="bottom")+
#   theme(legend.direction="horizontal")+
#   theme(axis.text.x=element_text(angle=-90))
```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r, fig.width=8,fig.height=8,echo=FALSE}
# ggplot(data=GastroscoptTherap,aes(x=ProcPerformed,freq,fill=Endo_Endoscopist))+
#   geom_bar(stat="identity")+
#    theme(legend.position="bottom")+
#   theme(legend.direction="horizontal")+
#   theme(axis.text.x=element_text(angle=-90))
```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r, fig.width=8,fig.height=8,echo=FALSE}
# ggplot(data=ERCP,aes(x=ProcPerformed,freq,fill=Endo_Endoscopist))+
#   geom_bar(stat="identity")+
#    theme(legend.position="bottom")+
#   theme(legend.direction="horizontal")+
#   theme(axis.text.x=element_text(angle=-90))
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r, fig.width=8,fig.height=8,echo=FALSE}
# ggplot(data=LowerOscopy,aes(x=ProcPerformed,freq,fill=Endo_Endoscopist))+
#   geom_bar(stat="identity")+
#    theme(legend.position="bottom")+
#   theme(legend.direction="horizontal")+
#   theme(axis.text.x=element_text(angle=-90))
```